Figure 4b

### 2018-02-27 inst/tcga_survival/fiveYR.Rmd
survival analysis now fully incorporated

#### _Introduction_

#### _Methods_

@@

### 5 year survival analysis

>>>>

#### _Introduction_
Correlation analysis between the effects on the 5-year survival
probability of TP53-mutated samples, low lncTAM34a expression, and low
miR34a expression as indicated. For each variable the 5-year survival
probability was compared to the control group (negative values indicate lower
survival, positive values indicate higher survival). Spearman correlation
coefficients are given on top left of each plot. Each dot indicates one cancer
type. Boxplots on the bottom summarize the effects for
the parameter on the x-axis, with indication of P values, as calculated using
paired Wilcoxon signed rank test. Low expression was defined as TP53 non-
mutated samples having expression values in the bottom 10th percentile.

#### _Methods_
RNAseq data was downloaded from TCGA and processed as described previously. 
Briefly, RNAseq data were aligned to the human hg19 assembly and quantified 
using GENCODE (v19) annotated HTSeq-counts and FPKM normalizations. Expression 
data from miR34a and lncTAM34a (identified as RP3-510D11.2) were used for 
further analysis.

Survival analysis was performed on TCGA vital state and follow-up data,
downloaded from GDC on 27/10/2017 using the R survival package.

@@
